Synthesizing Verified Components~~~\\ for Cyber Assured Systems Engineering~ \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2021-08-01 paper/case-study.tex
Updated case-study; removed figure to shorten it and added some more motivation for it

In this section, we outline the application of the BriefCASE tool towards the development of a UAV surveillance system as a part of the DARPA CASE program.
The motivation here was to showcase the toolchain on an industrial scale problem, to see if the technology works, i.e. provides engineers with early validation of their model; provides early information about cyber-vulnerabilities and in the effectiveness of related mitigations; to show that the tool can handle the UXAS message format (a complex, real-world message format); and to validate the utility and capability of the toolchain.

%apply the BriefCASE tool towards the development of a UAV surveillance system in which 
The UAV receives commands from a ground station to conduct surveillance over a geographical region. In response, the UAV's on-board mission computer generates a flight plan consisting of a series of waypoints that the UAV must traverse to complete its mission. The UAV is also given a set of \textit{keep-in} and \textit{keep-out} zones that may constrain its flight path.

@@

The UAV and Ground Station software were deployed on ODROID XU4 hardware, and communicated with each other over ethernet.  The AMASE flight simulator, representing the Flight Control Computer was run on a Linux machine and connected to the UAV ODROID via a serial connection.  The UxAS implementation on the UAV was modified by adding malicious code that would prevent it from responding to Automation Requests or produce flight plans that would violate the operating region constraints.  Some of the Line Search Task messages transmitted from the Ground Station contained malformed messages that would modify the UxAS behavior. In addition, we modified the Ground Station to simulate a breach for our evaluation of the attestation transform.
%
We performed a set of tests on the initial system (\figref{fig:sw-initial}) prior to applying our cyber-resiliency mitigations in order to verify the effectiveness of the malicious code.  
A third party evaluator repeated the tests on the hardened system and % were able to 
demonstrated that our mitigations were successful.
The following scenarios were exercised (status messages from the high-assurance components in the hardened system are in \figref{fig:mitigation-output}):

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.8\columnwidth]{figs/mitigation-output.png}
	\caption{Cyber-resilient system response.} 
	\label{fig:mitigation-output} 
\end{figure}

>>>>

In this section, we outline the application of the BriefCASE tool towards the development of a UAV surveillance system as a part of the DARPA CASE program.
The motivation was to showcase the toolchain on an industrial scale problem, to see if the technology works, i.e. provides engineers with early validation of their model; provides early information about cyber-vulnerabilities and in the effectiveness of related mitigations; to show that the tool can handle the UXAS message format (a complex, real-world message format); and to validate the utility and capability of the toolchain.

%apply the BriefCASE tool towards the development of a UAV surveillance system in which 
In this surveillance system, the UAV receives commands from a ground station to conduct surveillance over a geographical region. In response, the UAV's on-board mission computer generates a flight plan consisting of a series of waypoints that the UAV must traverse to complete its mission. The UAV is also given a set of \textit{keep-in} and \textit{keep-out} zones that may constrain its flight path.

@@

The UAV and Ground Station software were deployed on ODROID XU4 hardware, and communicated with each other over ethernet.  The AMASE flight simulator, representing the Flight Control Computer was run on a Linux machine and connected to the UAV ODROID via a serial connection.  The UxAS implementation on the UAV was modified by adding malicious code that would prevent it from responding to Automation Requests or produce flight plans that would violate the operating region constraints.  Some of the Line Search Task messages transmitted from the Ground Station contained malformed messages that would modify the UxAS behavior. In addition, we modified the Ground Station to simulate a breach for our evaluation of the attestation transform.
%
We performed a set of tests on the initial system (\figref{fig:sw-initial}) prior to applying our cyber-resiliency mitigations in order to verify the effectiveness of the malicious code.  
A third party evaluator repeated the tests on the hardened system and % were able to 
demonstrated that our mitigations were successful.
%The following scenarios were exercised (status messages from the high-assurance components in the hardened system are in \figref{fig:mitigation-output}):
The following scenarios were exercised:

@@

% \begin{figure}[h]
% 	\centering
% 	\includegraphics[width=0.8\columnwidth]{figs/mitigation-output.png}
% 	\caption{Cyber-resilient system response.} 
% 	\label{fig:mitigation-output} 
% \end{figure}
